---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: this is a toy package created for learning purposes, based on instructions
in the book R packages (2nd edition).

# regexcite

<!-- badges: start -->
<!-- badges: end -->

The goal of regexcite is to make regular expressions more exciting!
It provides convenience functions to make some common tasks ith string manipulation
and regular expressions easier.

## Installation

You can install the development version of regexcite from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marwinar/regexcite")
```

## Usage

A common task when dealing with strings is the need to split a single string
into many parts, based on a separator. This is what `base::strsplit()` and
`stringr::strsplit()` do.

```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

Notice how the return value is a **list** of length one, where the first element
holds the parts. Often the shape of this output is inconvenient and we want the
unlisted version.

That's exactly what `regexcite::str_split_one()` does.

```{r}
library(regexcite)

str_split_one(x, pattern = ",")
```
Use `str_split_one()` when the input is known to be a single string.
For safety, it will error if its input has length greater than one.

`str_split_one()` is built on `stringr::str_split()`, so you can use it's `n`
argument and such.

```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```

